### 2017-11-23 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{scopes}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{gensymb}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

@@

\begin{document}
\begin{center}
\underline{\huge Thermal Physics}
\end{center}
\section{Differences between heat and temperature}
\begin{tabular}{|c|c|c|}
\hline
&Heat&Temperature\\
\hline
Definition&Thermal energy(transferred from hot to cooler places)&A comparative measure of how hot something is\\
\hline
Unit&Joule&Kelvin\\
\hline
Measured using&Joulemeter&Thermometer\\
\hline
\end{tabular}
\section{Graph of heating water}
\includegraphics[width=3in]{water_heat_curve.jpg}
\section{Specific heat capacity}
\textbf{Specific heat capacity} - The energy needed to raise the temperature of 1kg of a material by 1K\\
\\
$c=\dfrac{Q}{m\Delta\theta}$\\
\\
c=Specific heat capacity - $Jkg^{-1} \ \degree C$\\
m=Mass - $kg$\\
$\Delta\theta$ = Temperature change - $\degree C$\\
Q = Heat energy - $J$
\subsection{Latent heat}
\textbf{Specific latent heat of fusion, $\mathbf{L_f}$} \quad \textcolor{red}{$Q=mL_f$}\\
The energy needed to change 1kg of a solid to a liquid without a temperature change\\
\\
\textbf{Specific latent heat of vaporisation, $\mathbf{L_v}$} \quad \textcolor{red}{$Q=mL_v$}\\
The energy needed to change 1kg of a liquid to a vapour without a temperature change
\subsection{How to determine the specific heat capacity of a metal}
\includegraphics[width=2in]{SHC_Experiment.jpg}
\begin{enumerate}
\item Set up the experiment with a voltmeter and ammeter to determine the electrical power of the heater
\item Allow time for the heat to conduct through the metal (until there is a temperature rise)
\item Start a stopclock, record the V, I and temperature
\item Record V, I and T every 2 minutes for 20 minutes
\end{enumerate}
\section{Boyle's law}
Boyle's law - Pressure is inversely proportional to volume\\
Gases - Free moving particles, no forces\\
$$\text{Boyle's law: } P=kV^{g}$$
$$\ln(P)=\ln(k)+g\ln(V)$$
$$\text{This is in the form y=c+mx}$$
\end{document}

>>>>

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{scopes}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{gensymb}
\usepackage{tabularx}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

@@

\begin{document}
\begin{center}
\underline{\huge Thermal Physics}
\end{center}
\section{Differences between heat and temperature}
\begin{tabular}{|c|c|c|}
\hline
&Heat&Temperature\\
\hline
Definition&Thermal energy(transferred from hot to cooler places)&A comparative measure of how hot something is\\
\hline
Unit&Joule&Kelvin\\
\hline
Measured using&Joulemeter&Thermometer\\
\hline
\end{tabular}
\section{Graph of heating water}
\includegraphics[width=3in]{water_heat_curve.jpg}
\section{Specific heat capacity}
\textbf{Specific heat capacity} - The energy needed to raise the temperature of 1kg of a material by 1K\\
\\
$c=\dfrac{Q}{m\Delta\theta}$\\
\\
c=Specific heat capacity - $Jkg^{-1} \ \degree C$\\
m=Mass - $kg$\\
$\Delta\theta$ = Temperature change - $\degree C$\\
Q = Heat energy - $J$
\subsection{Latent heat}
\textbf{Specific latent heat of fusion, $\mathbf{L_f}$} \quad \textcolor{red}{$Q=mL_f$}\\
The energy needed to change 1kg of a solid to a liquid without a temperature change\\
\\
\textbf{Specific latent heat of vaporisation, $\mathbf{L_v}$} \quad \textcolor{red}{$Q=mL_v$}\\
The energy needed to change 1kg of a liquid to a vapour without a temperature change
\subsection{How to determine the specific heat capacity of a metal}
\includegraphics[width=2in]{SHC_Experiment.jpg}
\begin{enumerate}
\item Set up the experiment with a voltmeter and ammeter to determine the electrical power of the heater
\item Allow time for the heat to conduct through the metal (until there is a temperature rise)
\item Start a stopclock, record the V, I and temperature
\item Record V, I and T every 2 minutes for 20 minutes
\end{enumerate}
\section{Gas laws}
\subsection{Boyle's law}
Boyle's law - Pressure is inversely proportional to volume\\
Gases - Free moving particles, no forces\\
$$\text{Boyle's law: } P=kV^{g}$$
$$\ln(P)=\ln(k)+g\ln(V)$$
$$\text{This is in the form y=c+mx}$$
\subsection{Summary of gas laws}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
Law&Proportionality&Constant&Equation\\
\hline
Boyle's&$p\propto\dfrac{1}{v}$&Temperature, moles&$p_1v_1=p_2v_2$\\
\hline
Charles'&$V\propto T$&Pressure, moles&$\dfrac{v_1}{T_1}=\dfrac{v_2}{T_2}$\\
\hline
Gay-Lussac&$p\propto T$&Volume, moles&$\dfrac{p_1}{T_1}=\dfrac{P_2}{T_2}$\\
\hline
\end{tabularx}
\newpage
\subsection{Ideal Gas equation}
$$pV=nRT$$\\
\\
p=Pressure(Pascals)\\
V=Volume($m^3$)\\
n=Number of moles\\
R=Universal gas constant=$8.31JK^{-1}mol^{-1}$\\
T=Temperature(K)
\end{document}
